---
title: 'How far ahead is India?'
output: 
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: lux
      warning: '#010101'
    orientation: rows
    source_code: https://github.com/gafnts/brics-dashboard
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
pacman::p_load(
  flexdashboard, shiny, dplyr, arrow, here, stringr, lubridate, echarts4r, bslib
)

import <- function(path) read_feather(here('data', 'clean', path))
brics <- import('brics.feather')
indicators <- import('indicators.feather')
wdi <- import('wdi.feather')
un <- import('un.feather')

countries <- brics |> filter(iso2c != 'IN') |> pull(flag_country)
```

```{r functions}
value_caption <- function(name, caption = '* 2010 - 2020 average') {
  htmltools::HTML(
    glue::glue("<p style = 'font-size : 15.5px;'> {name} </p><br/> 
                 <p style = 'font-size : 10px;'> {caption} </p>")
  )
}

ten_year_mean <- function(country, var, percent = TRUE) {
    if (percent == TRUE) {
      wdi |> 
      filter(iso2c == {{country}}) |> 
      filter(year >= 2010 & year <= 2020) |> 
      summarise(mean = round(mean({{var}}), 2)) |> 
      mutate(mean = paste0(mean, '%'))
    } else {
      wdi |> 
      filter(iso2c == {{country}}) |> 
      filter(year >= 2010 & year <= 2020) |> 
      summarise(mean = round(mean({{var}}), 2))
    }
}

country_filter <- function(...) {
    input$countries |> 
    as_tibble() |> 
    left_join(brics, by = c('value' = 'flag_country')) |> 
    pull(iso2c)
}

indicator_filter <- function(input, yank) {
    input |> 
    as_tibble() |> 
    left_join(indicators, by = c('value' = 'display')) |> 
    pull({{yank}})
}

bar_chart <- function(data = wdi, country, indicator, color, forecast = FALSE) {
    if (forecast == FALSE) {
      data |> 
      filter(iso2c == {{country}}) |> 
      select(year, ` ` = {{indicator}}) |> 
      mutate(year = as_date(paste(year, '01', '01', sep = '-'))) |> 
      e_charts(year) |> 
      e_bar(` `, color = color) |> 
      e_legend(FALSE) |> 
      e_tooltip(trigger = "axis")
    } else {
      data |> 
      filter(iso2c == {{country}}) |> 
      select(year, ` ` = {{indicator}}, color) |> 
      mutate(year = as_date(paste(year, '01', '01', sep = '-'))) |> 
      group_by(color) |> 
      e_charts(year) |> 
      e_area(` `) |> 
      e_legend(FALSE) |> 
      e_tooltip(trigger = "axis") |>
      e_color(
        c(forecast_color, color)
      )
    }
}
```

```{r colors}
india_color <- '#4B4B4B'
country_color <- '#FFCF04'
forecast_color <- '#C1C4C7'
```


```{css}
.shiny-text-output {  /* chart_title  */
  font-size: 16px;
  font-weight: bold;
}
```

Economic indicators
=======================================================================

Sidebar {.sidebar data-width=265}
-------------------------------------

```{r}
econ_ind <- 
  indicators |> 
  filter(str_detect(dashboard, 'Economic')) |> 
  slice(6, 7, 4, 5) |> 
  pull(display)

selectInput(
  inputId = 'countries',
  label = 'Compare India with:', 
  choices = countries, 
  selected = countries[1]
)

selectInput(
  inputId = 'econ_indicators',
  label = 'Select an economic indicator:', 
  choices = econ_ind, 
  selected = econ_ind[1]
)
```

This dashboard will let you explore how India compares to the other [BRICS](https://en.wikipedia.org/wiki/BRICS) economies as measured by key economic, social and demographic indicators in an easy-to-use interface. <br><br><br>

<font size = '1px'> Data: [World Development Indicators](https://data.worldbank.org/)
<br> Forecasts: [World Population Prospects](https://population.un.org/wpp/)
<br><br> Disclaimer: Some missing data has been imputed using KNN. </font>

Row: Title
-----------------------------------------------------------------------

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = brics |> filter(iso2c == 'IN') |> pull(flag_country),
    icon = NULL,
    color = 'warning'
  )
})
```

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = input$countries,
    icon = NULL,
    color = country_color
  )
})
```

Row: Value boxes
-----------------------------------------------------------------------

### Inflation {.value-box}

```{r}
renderValueBox({
  inf <- ten_year_mean('IN', inflation)
  
  valueBox(
    value = inf,
    caption = value_caption('Inflation *'),
    icon = NULL,
    color = 'warning'
  )
})
```

### Real interest rate * {.value-box}

```{r}
renderValueBox({
  i <- ten_year_mean('IN', real_interest_rate)
  
  valueBox(
    value = i,
    icon = NULL,
    color = 'warning'
  )
})
```

### Unemployment * {.value-box}

```{r}
renderValueBox({
  unem <- ten_year_mean('IN', unemployment)
  
  valueBox(
    value = unem,
    icon = NULL,
    color = 'warning'
  )
})
```

### Inflation {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  inf <- ten_year_mean(country, inflation)
  
  valueBox(
    value = inf,
    caption = value_caption('Inflation *'),
    icon = NULL,
    color = country_color
  )
})
```

### Real interest rate * {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  i <- ten_year_mean(country, real_interest_rate)
  
  valueBox(
    value = i,
    icon = NULL,
    color = country_color
  )
})
```

### Unemployment * {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  unem <- ten_year_mean(country, unemployment)
  
  valueBox(
    value = unem,
    icon = NULL,
    color = country_color
  )
})
```

Row
-----------------------------------------------------------------------

```{r}
econ_plot_title <- 
  shiny::renderText({indicator_filter(
      input = input$econ_indicators, 
      yank = original_name
      )})
```

### `r econ_plot_title`

```{r}
renderEcharts4r({
   indicator <- indicator_filter(
      input = input$econ_indicators, 
      yank = name
      )
  
    bar_chart(
      data = wdi,
      country = 'IN',
      indicator = indicator,
      color = india_color
    )
  })
```

### `r econ_plot_title` 

```{r}
renderEcharts4r({
    country <- country_filter('flag_country')
    
    indicator <- indicator_filter(
      input = input$econ_indicators, 
      yank = name
      )
    
    bar_chart(
      data = wdi,
      country = country,
      indicator = indicator,
      color = country_color
    )
  })
```

Social development
=======================================================================

sidebar {.sidebar data-width=265}
-------------------------------------
<br>

```{r}
social_ind <- 
  indicators |> 
  filter(str_detect(dashboard, 'Social')) |> 
  slice(7, 8, 4, 2) |>
  pull(display)

selectInput(
  inputId = 'social_indicators',
  label = 'Select a social indicator:', 
  choices = social_ind,
  selected = social_ind[1]
)
```

This dashboard will let you explore how India compares to the other [BRICS](https://en.wikipedia.org/wiki/BRICS) economies as measured by key economic, social and demographic indicators in an easy-to-use interface. <br><br><br>

<font size = '1px'> Data: [World Development Indicators](https://data.worldbank.org/)
<br> Forecasts: [World Population Prospects](https://population.un.org/wpp/)
<br><br> Disclaimer: Some missing data has been imputed using KNN. </font>

Row: Title
-----------------------------------------------------------------------

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = brics |> filter(iso2c == 'IN') |> pull(flag_country),
    icon = NULL,
    color = 'warning'
  )
})
```

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = input$countries,
    icon = NULL,
    color = country_color
  )
})
```

Row: Value boxes
-----------------------------------------------------------------------

### Life expectancy {.value-box}

```{r}
renderValueBox({
  life <- ten_year_mean('IN', life_expectancy_at_birth, percent = FALSE)
  
  valueBox(
    value = life,
    caption = value_caption(
      name = 'Life expectancy (years) *',
      caption = '* 2010 - 2020 average'
    ),
    icon = NULL,
    color = 'warning'
  )
})
```

### Mortality rate * {.value-box}

```{r}
renderValueBox({
  mortality <- ten_year_mean('IN', mortality_rate, percent = FALSE)
  
  valueBox(
    value = mortality,
    caption = value_caption(
      name = 'Mortality rate (under-five) *',
      caption = '(per 1,000 live births)'
    ),
    icon = NULL,
    color = 'warning'
  )
})
```

### Adolescent fertility rate * {.value-box}

```{r}
renderValueBox({
  fertility <- ten_year_mean('IN', adolescent_fertility_rate, percent = FALSE)
  
  valueBox(
    value = fertility,
    caption = value_caption(
    name = 'Adolescent fertility rate *',
    caption = '(births per 1,000 women)'
    ),
    icon = NULL,
    color = 'warning'
  )
})
```

### Life expectancy {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  life <- ten_year_mean(country, life_expectancy_at_birth, percent = FALSE)
  
  valueBox(
    value = life,
    caption = value_caption(
    name = 'Life expectancy (years) *',
    caption = '* 2010 - 2020 average'
    ),
    icon = NULL,
    color = country_color
  )
})
```

### Mortality rate * {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  mortality <- ten_year_mean(country, mortality_rate, percent = FALSE)
  
  valueBox(
    value = mortality,
    caption = value_caption(
    name = 'Mortality rate (under-five) *',
    caption = '(per 1,000 live births)'
    ),
    icon = NULL,
    color = country_color
  )
})
```

### Adolescent fertility rate * {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  fertility <- ten_year_mean(country, adolescent_fertility_rate, percent = FALSE)
  
  valueBox(
    value = fertility,
    caption = value_caption(
    name = 'Adolescent fertility rate *',
    caption = '(births per 1,000 women)'
    ),
    icon = NULL,
    color = country_color
  )
})
```

Row
-----------------------------------------------------------------------

```{r}
social_plot_title <- 
  shiny::renderText({indicator_filter(
      input = input$social_indicators, 
      yank = original_name
      )})
```

### `r social_plot_title`

```{r}
renderEcharts4r({
   indicator <- indicator_filter(
      input = input$social_indicators, 
      yank = name
      )
  
    bar_chart(
      data = wdi,
      country = 'IN',
      indicator = all_of(indicator),
      color = india_color
    )
  })
```

### `r social_plot_title` 

```{r}
renderEcharts4r({
    country <- country_filter('flag_country')
    
    indicator <- indicator_filter(
      input = input$social_indicators, 
      yank = name
      )
    
    bar_chart(
      data = wdi,
      country = country,
      indicator = all_of(indicator),
      color = country_color
    )
  })
```


Climate change
=======================================================================

sidebar {.sidebar data-width=265}
-------------------------------------
<br>

```{r}
climate_ind_one <- 
  indicators |> 
  filter(str_detect(dashboard, 'Climate')) |> 
  slice(1, 2) |> 
  pull(display)

climate_ind_two <- 
  indicators |> 
  filter(str_detect(dashboard, 'Climate')) |> 
  slice(3, 4) |> 
  pull(display)

selectInput(
  inputId = 'climate_indicators_one',
  label = 'Select two environmental indicators:', 
  choices = climate_ind_one,
  selected = climate_ind_one[1]
)

selectInput(
  inputId = 'climate_indicators_two',
  label = NULL, 
  choices = climate_ind_two,
  selected = climate_ind_two[1]
)
```

This dashboard will let you explore how India compares to the other [BRICS](https://en.wikipedia.org/wiki/BRICS) economies as measured by key economic, social and demographic indicators in an easy-to-use interface. <br><br><br>

<font size = '1px'> Data: [World Development Indicators](https://data.worldbank.org/)
<br> Forecasts: [World Population Prospects](https://population.un.org/wpp/)
<br><br> Disclaimer: Some missing data has been imputed using KNN. </font>

Row: Title
-----------------------------------------------------------------------

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = brics |> filter(iso2c == 'IN') |> pull(flag_country),
    icon = NULL,
    color = 'warning'
  )
})
```

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = input$countries,
    icon = NULL,
    color = country_color
  )
})
```

Row
-----------------------------------------------------------------------

```{r}
climate_plot_title_one <- 
  shiny::renderText({indicator_filter(
      input = input$climate_indicators_one, 
      yank = original_name
      )})
```

### `r climate_plot_title_one`

```{r}
renderEcharts4r({
   indicator <- indicator_filter(
      input = input$climate_indicators_one, 
      yank = name
      )
  
    bar_chart(
      data = wdi,
      country = 'IN',
      indicator = all_of(indicator),
      color = india_color
    )
  })
```

### `r climate_plot_title_one` 

```{r}
renderEcharts4r({
    country <- country_filter('flag_country')
    
    indicator <- indicator_filter(
      input = input$climate_indicators_one, 
      yank = name
      )
    
    bar_chart(
      data = wdi,
      country = country,
      indicator = all_of(indicator),
      color = country_color
    )
  })
```

Row
-----------------------------------------------------------------------

```{r}
climate_plot_title_two <- 
  shiny::renderText({indicator_filter(
      input = input$climate_indicators_two, 
      yank = original_name
      )})
```

### `r climate_plot_title_two`

```{r}
renderEcharts4r({
   indicator <- indicator_filter(
      input = input$climate_indicators_two, 
      yank = name
      )
  
    bar_chart(
      data = wdi,
      country = 'IN',
      indicator = all_of(indicator),
      color = india_color
    )
  })
```

### `r climate_plot_title_two` 

```{r}
renderEcharts4r({
    country <- country_filter('flag_country')
    
    indicator <- indicator_filter(
      input = input$climate_indicators_two, 
      yank = name
      )
    
    bar_chart(
      data = wdi,
      country = country,
      indicator = all_of(indicator),
      color = country_color
    )
  })
```

Demography
=======================================================================

sidebar {.sidebar data-width=265}
-------------------------------------
<br>

```{r}
demo_ind <- 
  indicators |> 
  filter(str_detect(dashboard, 'Demo')) |> 
  slice(4, 5, 6, 7) |> 
  pull(display)

selectInput(
  inputId = 'demo_indicators',
  label = 'Select a demographic indicator:', 
  choices = demo_ind,
  selected = demo_ind[1]
)
```

This dashboard will let you explore how India compares to the other [BRICS](https://en.wikipedia.org/wiki/BRICS) economies as measured by key economic, social and demographic indicators in an easy-to-use interface. <br><br><br>

<font size = '1px'> Data: [World Development Indicators](https://data.worldbank.org/)
<br> Forecasts: [World Population Prospects](https://population.un.org/wpp/)
<br><br> Disclaimer: Some missing data has been imputed using KNN. </font>

Row: Title
-----------------------------------------------------------------------

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = brics |> filter(iso2c == 'IN') |> pull(flag_country),
    icon = NULL,
    color = 'warning'
  )
})
```

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = input$countries,
    icon = NULL,
    color = country_color
  )
})
```

Row: Value boxes
-----------------------------------------------------------------------

### Population growth {.value-box}

```{r}
renderValueBox({
  growth <- ten_year_mean('IN', population_growth)
  
  valueBox(
    value = growth,
    caption = value_caption(
      name = 'Population growth rate *',
      caption = '* 2010 - 2020 average'
    ),
    icon = NULL,
    color = 'warning'
  )
})
```

### Rural population * {.value-box}

```{r}
renderValueBox({
  rural <- ten_year_mean('IN', rural_population)
  
  valueBox(
    value = rural,
    caption = value_caption(
      name = 'People living in rural areas *',
      caption = '(% of total population)'
    ),
    icon = NULL,
    color = 'warning'
  )
})
```

### Urban population * {.value-box}

```{r}
renderValueBox({
  urban <- ten_year_mean('IN', urban_population)
  
  valueBox(
    value = urban,
    caption = value_caption(
    name = 'People living in urban areas *',
    caption = '(% of total population)'
    ),
    icon = NULL,
    color = 'warning'
  )
})
```

### Population growth {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  growth <- ten_year_mean(country, population_growth)
  
  valueBox(
    value = growth,
    caption = value_caption(
    name = 'Population growth rate *',
    caption = '* 2010 - 2020 average'
    ),
    icon = NULL,
    color = country_color
  )
})
```

### Rural population * {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  rural <- ten_year_mean(country, rural_population)
  
  valueBox(
    value = rural,
    caption = value_caption(
    name = 'People living in rural areas *',
    caption = '(% of total population)'
    ),
    icon = NULL,
    color = country_color
  )
})
```

### Urban population * {.value-box}

```{r}
renderValueBox({
  country <- country_filter()
  urban <- ten_year_mean(country, urban_population)
  
  valueBox(
    value = urban,
    caption = value_caption(
    name = 'People living in urban areas *',
    caption = '(% of total population)'
    ),
    icon = NULL,
    color = country_color
  )
})
```

Row
-----------------------------------------------------------------------

```{r}
demo_plot_title <- 
  shiny::renderText({indicator_filter(
      input = input$demo_indicators, 
      yank = original_name
      )})
```

### `r demo_plot_title`

```{r}
renderEcharts4r({
   indicator <- indicator_filter(
      input = input$demo_indicators, 
      yank = name
      )
  
    bar_chart(
      data = un,
      country = 'IN',
      indicator = all_of(indicator),
      color = india_color,
      forecast = TRUE
    )
  })
```

### `r demo_plot_title` 

```{r}
renderEcharts4r({
    country <- country_filter('flag_country')
    
    indicator <- indicator_filter(
      input = input$demo_indicators, 
      yank = name
      )
    
    bar_chart(
      data = un,
      country = country,
      indicator = all_of(indicator),
      color = country_color,
      forecast = TRUE
    )
  })
```
